---
title: "Leaf shape microbiome"
author: "Julia Boyle"
date: "2023-07-31"
output: html_document
---
#Packages
```{r}
library(pander)
library(ape)
library(microbiomeSeq)
library(ranacapa)
library(adespatial)
library(plotly)
library(philr)
library(MicrobeR)
library(microbiome)
library(microbiomeutilities)
library(qiime2R)
library(phyloseq)
library(ANCOMBC)
library(plyr)
library(tidyverse)
library(car)
library(vegan)
library(RColorBrewer) 
library(randomcoloR)
library(cowplot)
library(lmerTest)
library(insight)
library(lme4)
library(compositions)
library(zCompositions)
library(phyloseqCompanion)
library(CoDaSeq)
library(microshades)#color blind friendly shades
library(speedyseq)
library(patchwork)
library(viridis)
library(picante)
```



# Reading in data
```{r}
#Reading in metadata as it's own file
micrometa<- read.csv('ipomoea-taxa-metadata-allnumbers.csv',header = TRUE) #full metadata
micrometa$Shape<-factor(micrometa$Shape, levels=c("L", "M", "H"))
metadata<-read.table('ipomoea_metadata.tsv', header=TRUE, row.names = 1) #this only has plants that survived, so not all numbers between 1-240
metadata$Shape<-factor(metadata$Shape, levels=c("L", "M", "H"))
metadata$Line<-as.factor(metadata$Line)
metadata$Germination_cohort<-as.factor(metadata$Germination_cohort)
str(metadata)
metadata
featuretable<- read.csv('table-try3-10readsmin-filtered-cyano-mito.csv',row.names = 1, check.names = FALSE, header = TRUE) #this is the feature table as a .csv file
taxonomy<- read.csv('taxonomy_try3.csv') #the taxonomy file as a .csv file


phyglory <- qza_to_phyloseq("table-try3-10readsmin-filtered-cyano-mito-glory.qza", "rooted-tree-try3-glory.qza", "taxonomy-try3-glory.qza","ipomoea_metadata.tsv") 

sample_data(phyglory)$FloweringDOY<-as.factor(sample_data(phyglory)$FloweringDOY) 
sample_data(phyglory)$Days_to_flowering_factor<-as.factor(sample_data(phyglory)$Days_to_flowering)
sample_data(phyglory)$Line<-as.factor(sample_data(phyglory)$Line) 
sample_data(phyglory)$Shape<-factor(sample_data(phyglory)$Shape, levels=c("L", "M", "H"))
sample_data(phyglory)['sample_id'] <- row.names(sample_data(phyglory)) 
str(phyglory)
sample_data(phyglory)

# check for features of data  
summarize_phyloseq(phyglory)
print_ps(phyglory)
summary(sample_sums(phyglory))
ntaxa(phyglory)
nsamples(phyglory)
sample_names(phyglory)[1:5]  
rank_names(phyglory)  
sample_variables(phyglory)  
otu_table(phyglory)[1:5, 1:5]  
tax_table(phyglory)[1:10, 1:4]

#Checking taxa prevalence at phylum level
plot_taxa_prevalence(phyglory, "Phylum")
```

# Rarefaction of data
Does the order matter of prevalence aggregation and rarefying step? Which one is more correct?
```{r}
# set seed
set.seed(1)
subsamples <- seq(0, 23100, by=100)[-1]
phygloryrarefactioncurve <- plot_alpha_rcurve(phyglory, index="observed", #phyglory is the file
                       subsamples = subsamples,
                       lower.conf = 0.5, 
                       upper.conf = 0.5,
                       group="Shape",
                       label.color = "brown3",
                       label.size = 3,
                       label.min = TRUE) 
print(phygloryrarefactioncurve) #M shape plateaus at a lower observed species number
```

```{r}
phyglory_rarefy <- rarefy_even_depth(phyglory, rngseed=1, sample.size=0.4*median(sample_sums(phyglory)), replace=F) # approx 1809 reads
summarize_phyloseq(phyglory_rarefy)
ntaxa(phyglory_rarefy)
nsamples(phyglory_rarefy)
```

#Centered log ratio transformation 
```{r}
#ASV feature table
featuretableCLR<-clr(featuretable+1) #add 1 to avoid taking log of 0, use compositions package
featuretableCLR<-as.data.frame(featuretableCLR)
featuretableCLR

#aggregated by Genus
phyglory_gen <- microbiome::aggregate_rare(phyglory, level = "Genus", detection = 0/100, prevalence = 30/100)#must be 0% relative abundance, and appear in at least 30% of samples
featuretableCLR_gen<-as.data.frame(otu_table(phyglory_gen))
write.csv(featuretableCLR_gen, "phygloryCLRGenfeaturetable.csv")#transposed manually in excel, rows for Other and Unknown genera removed
featuretableCLRgen<-read.csv('phygloryCLRGenfeaturetable.csv',row.names = 1, check.names = FALSE, header = TRUE)
featuretableCLRgen<-clr(featuretableCLRgen+1) #add 1 to avoid taking log of 0
featuretableCLRgen<-as.data.frame(featuretableCLRgen)
featuretableCLRgen
```

# Leaf shape statistics
## Leaf area
```{r}
hist(micrometa$Leaf_area_cm2)
summary(lmer(Leaf_area_cm2~Shape+Germination_cohort + (1|Line) + (1|Block), data=micrometa))
Anova((lmer(Leaf_area_cm2~Shape+Germination_cohort + (1|Line) + (1|Block), data=micrometa)), type=3)

area<-metadata%>% 
ggplot(aes(x=Germination_cohort, y=Leaf_area_cm2, fill=Shape))+
  geom_boxplot()+ theme_classic() + ylab('Leaf area (cm^2)')+xlab('Germination cohort') +scale_fill_manual(labels = c("Lobe", "Heterozygote", "Whole"), values = c("#00CCCC", "#9999FF", "#FF3333"))
```
## Circularity
"4π×([Area]/([Perimeter]2)) with a value of 1.0 indicating a perfect circle. As the value approaches 0.0, it indicates an increasingly elongated shape."
```{r}
hist(micrometa$Circularity)
Anova((lmer(Circularity~Shape+Germination_cohort + (1|Line) + (1|Block), data=micrometa)), type=3)

circularity<-metadata%>% 
ggplot(aes(x=Shape, y=Circularity, fill=Shape))+
  geom_boxplot()+ theme_classic() + ylab('Circularity')+scale_fill_manual(labels = c("Lobe", "Heterozygote", "Whole"), values = c("#00CCCC", "#9999FF", "#FF3333")) + scale_x_discrete(limits=c("L","M","H"), labels=c("Lobe", "Heterozygote", "Whole"))+theme(legend.position = "none")

```
## Between cohorts
```{r}
chisq.test(x=micrometa$Germination_cohort, y=micrometa$Shape) #No significant differences in leaf genotypes between cohorts
chisq.test(x=micrometa$Block, y=micrometa$Shape) #no sig differences in leaf shape genotypes between blocks
```


# Composition plots
Family level
```{r}
#making relative abundances objects for different taxonomic levels
phyglory_fam <- microbiome::aggregate_rare(phyglory, level = "Family", detection = 10/100, prevalence = 30/100)
phyglory.fam.rel <- microbiome::transform(phyglory_fam, "compositional")
phyglory.fam.rel <- phyglory %>%
  aggregate_rare(level = "Family", detection = 10/100, prevalence = 30/100) %>%
  microbiome::transform(transform = "compositional")

phyglory.fam.rel.germ1<-subset_samples(phyglory.fam.rel, Germination_cohort%in%c("First"))
phyglory.fam.rel.germ2<-subset_samples(phyglory.fam.rel, Germination_cohort%in%c("Second"))

#palettegood <- distinctColorPalette(50)

leaf_germ1<-plot_composition(phyglory.fam.rel.germ1, sample.sort = "Sphingomonadaceae", x.label = "Shape") + theme_cowplot()+ theme(legend.position = "none") +scale_fill_manual(values =palettegood) + theme(axis.text.x = element_blank(), axis.text.y=element_text(size=10)) + ggtitle("First germination cohort") + theme(legend.title = element_text(size = 5), axis.text = element_text(size=10) )+xlab("Samples")
leaf_germ1

leaf_germ2<-plot_composition(phyglory.fam.rel.germ2, sample.sort = "Sphingomonadaceae", x.label = "Shape") + theme_cowplot() +scale_fill_manual(values =palettegood) + theme(axis.text.x = element_blank(), axis.text.y=element_text(size=10)) + ggtitle("Second germination cohort") + theme(legend.title = element_text(size = 15), axis.text = element_text(size=10) )+xlab("Samples")+ guides(fill=guide_legend(title="Bacterial Family"))
leaf_germ2
```

Get relative abundance of different families per sample for downstream purposes
```{r}
genera_relabund<-phyglory_rarefy %>% tax_glom(taxrank = "Genus") %>% 
        transform_sample_counts(function(x) {x/sum(x)}) %>% psmelt() %>% 
        dplyr::select(Genus, Sample, Abundance) %>% spread(Sample, Abundance)
tgenera_relabund = setNames(data.frame(t(genera_relabund[,-1])), genera_relabund[,1])
tgenera_relabund

rarefiedmeta<-as.data.frame(sample_data(phyglory_rarefy))
vector<-rarefiedmeta$sample_id #get order of phyloseq metadata samples

tgenera_relabund_sorted<-tgenera_relabund %>%
  slice(match(vector, rownames(tgenera_relabund))) #reorder the dataframe to be the same order as the phyloseq metadata

tgenera_relabund_sorted$Methylobacterium

sample_data(phyglory_rarefy)$Methylobacterium_relabundance<-tgenera_relabund_sorted$Methylobacterium
sample_data(phyglory_rarefy)$Sphingomonas_relabundance<-tgenera_relabund_sorted$Sphingomonas
sample_data(phyglory_rarefy)$Agrobacterium_relabundance<-tgenera_relabund_sorted$Agrobacterium
sample_data(phyglory_rarefy)$Deinococcus_relabundance<-tgenera_relabund_sorted$Deinococcus
sample_data(phyglory_rarefy)$Pseudomonas_relabundance<-tgenera_relabund_sorted$Pseudomonas
sample_data(phyglory_rarefy)$Arthrobacter_relabundance<-tgenera_relabund_sorted$Arthrobacter
```

# Core microbiome
```{r}
phyglory_core <- microbiome::aggregate_rare(phyglory_rarefy, level = "Genus", detection = 0/100, prevalence = 80/100)
core_members(phyglory_core)
```


# Alpha diversities
plot
```{r}
gloryrich<-estimate_richness(phyglory_rarefy)
gloryrich<-cbind(gloryrich, sample_data(phyglory_rarefy))
a.divglory<-gloryrich %>% 
  ggplot(aes(x=Germination_cohort, y=Observed, fill=Germination_cohort))+geom_boxplot()+theme_cowplot() +theme(axis.text.x = element_text(size=13), legend.position="none") +xlab("Germination Cohort") + scale_fill_manual("Germination_cohort", values=c("#FF9900", "#99CC33"))+ ylab("Observed richness")
a.divglory
```
statistical test
```{r}
gloryrichness<-estimate_richness(phyglory_rarefy)
gloryrichness
hist(gloryrichness$Shannon)
hist(log(gloryrichness$Observed))

#shannon
Anova((lmer(Shannon~sample_data(phyglory_rarefy)$Shape+sample_data(phyglory_rarefy)$Germination_cohort + (1|sample_data(phyglory_rarefy)$Line) + (1|sample_data(phyglory_rarefy)$Block), data=gloryrichness)), type=3)

#Observed
Anova((lmer(log(Observed)~sample_data(phyglory_rarefy)$Shape+sample_data(phyglory_rarefy)$Germination_cohort + (1|sample_data(phyglory_rarefy)$Line) + (1|sample_data(phyglory_rarefy)$Block), data=gloryrichness)), type=3)
```

# Beta diversity
## PCoA
Leaf shape and germination cohort
```{r}
phyglory_rel_rare <- microbiome::transform(phyglory_rarefy, "compositional")
phyglory.ord.wuni_rare <- ordinate(phyglory_rel_rare, "PCoA", "unifrac", weighted=T)

b.div.wuniglory_rare <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Shape") + geom_point(size=3) + theme_cowplot() +ggtitle("")+ scale_color_manual("Leaf shape genotype",labels = c("Lobe", "Heterozygote", "Whole"), values = c("#00CCCC", "#9999FF", "#FF3333"))+ stat_ellipse()+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")
print(b.div.wuniglory_rare)

b.div.wuniglory_rareG <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Germination_cohort") + geom_point(size=3) +ggtitle("")  + scale_color_manual("Germination cohort",values=c("#FF9900", "#99CC33")) +theme_cowplot() + stat_ellipse()+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")
print(b.div.wuniglory_rareG)
```

Core taxa driving the variation
```{r}
b.div.wuniglory_methylo <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Methylobacterium_relabundance") + geom_point(size=3) + ggtitle("Methylobacterium") +theme_cowplot()+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")+scale_color_viridis(name="Relative abundance",discrete=FALSE, option="viridis")
print(b.div.wuniglory_methylo) #maybe driving PC1

b.div.wuniglory_sphingo <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Sphingomonas_relabundance") + geom_point(size=3) + ggtitle("Sphingomonas") +theme_cowplot()+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")+scale_color_viridis(name="Relative abundance",discrete=FALSE, option="viridis")
print(b.div.wuniglory_sphingo) #maybe driving PC2

b.div.wuniglory_dein <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Deinococcus_relabundance") + geom_point(size=3) + ggtitle("Deinococcus") +theme_cowplot()+scale_color_viridis(name="Relative abundance",discrete=FALSE, option="viridis")+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")
print(b.div.wuniglory_dein) #the couple dots out of place in methylobacterium plot

b.div.wuniglory_art <- plot_ordination(phyglory_rel_rare, phyglory.ord.wuni_rare, type= "samples", color= "Arthrobacter_relabundance") + geom_point(size=3) + ggtitle("Arthrobacter") +theme_cowplot()+scale_color_viridis(name="Relative abundance",discrete=FALSE, option="viridis")+xlab("Axis 1 [53.2%]")+ylab("Axis 2 [23.2%]")
print(b.div.wuniglory_art) #explains upper left corner
```

## Permanova and Permadisp
```{r}
set.seed(1)
wunifracdist<-distance(phyglory_rel_rare, method="wunifrac", type="samples")
braydist<-distance(phyglory_rel_rare, method="bray", type="samples")
wunifracdist

adonis2(wunifracdist ~ Shape+Germination_cohort, data = metaglory_rare, permutations=999) #sig germination cohort
anova(betadisper(d=wunifracdist, group=metaglory_rare$Germination_cohort)) #sig germination cohort. This means the sig germ cohort wunifrac distances could be due to dispersion differences

adonis2(braydist ~ Shape+Germination_cohort, data = metaglory_rare, permutations=999) #sig germination cohort
anova(betadisper(d=braydist, group=metaglory_rare$Germination_cohort)) #nonsig germination cohort, this suggests differences in dispersion are not responsible for differences in bray-curtis composition
```

Checking that having slightly uneven sample sizes in germ 1 and 2 does not affect the significance of our permanova and permadisp
```{r}
phyglory_rel_rareG1<-subset_samples(phyglory_rel_rare, Germination_cohort%in%c("First"))
phyglory_rel_rareG2<-subset_samples(phyglory_rel_rare, Germination_cohort%in%c("Second"))
phyglory_rel_rareG1 #77 samples
phyglory_rel_rareG2 #106 samples

sample_ps <- function(phyglory_rel_rareG2, FUN = sample, ...){ 
  ids <- sample_names(phyglory_rel_rareG2)
  sampled_ids <- FUN(ids, ...) #randomly sample from id sample numbers
  ps <- prune_samples(sampled_ids, phyglory_rel_rareG2) #prune germ2 to the randomized set
  ps_joined<-merge_phyloseq(ps, phyglory_rel_rareG1) #merge together germ1 with the reshuffled germ2
  return(ps_joined)
}
set.seed(1)
permanovalist <- list() #make empty lists for the test results
permadisplist_germ<-list()
permadisplist_shape<-list()
for (i in 1:100){ #try with reshuffling germ2 data 100 times
  ps_joined<-sample_ps(phyglory_rel_rareG2, size=77, replace=FALSE) #do the random shuffling so that germ2 only has 77 samples
  wunifracdistjoined<-distance(ps_joined, method="wunifrac", type="samples") #create the distance matrix
  permanovalist[[i]]<-(adonis2(wunifracdistjoined ~ Shape+Germination_cohort, data = as.data.frame(as.matrix(sample_data(ps_joined))), permutations=999))
  permadisplist_germ[[i]]<-(anova(betadisper(d=wunifracdistjoined, group=as.data.frame(as.matrix(sample_data(ps_joined)))$Germination_cohort)))
  permadisplist_shape[[i]]<-(anova(betadisper(d=wunifracdistjoined, group=as.data.frame(as.matrix(sample_data(ps_joined)))$Shape)))
}

#extract F and p from the permanova
permanova<-data.frame(matrix(unlist(permanovalist), nrow=length(permanovalist), byrow=TRUE))
permanova<- dplyr::select(permanova, X13, X14, X17, X18)
colnames(permanova) <- c("Shape_F", "Germ_F", "Shape_p", "Germ_p")
permanova

#extract F and p for the permadisp of germination
permadisp_germ<-data.frame(matrix(unlist(permadisplist_germ), nrow=length(permadisplist_germ), byrow=TRUE))
permadisp_germ<-dplyr::select(permadisp_germ, X7,X9)
colnames(permadisp_germ) <- c("Germ_F", "Germ_p" )
permadisp_germ

hist(permanova$Shape_p, breaks=12)
hist1<-hist(permanova$Germ_p)
hist2<-hist(permadisp_germ$Germ_p)
plot(hist1, xlab=("Germination cohort p value"), main=("PERMANOVA"))
plot(hist2, xlab=("Germination cohort p value"), main=("PERMADISP"))
```


# Estimating heritability
## Community wide metrics
```{r}
#getting species richness and ordination first 3 axes into one metadata file
metadataphyR<-as.data.frame(sample_data(phyglory_rarefy))
gloryrichness_rarefied<-estimate_richness(phyglory_rarefy) #generating observed and shannon 
metadataphyR$ObservedRich<-gloryrichness_rarefied$Observed
metadataphyR$Shannon<-gloryrichness_rarefied$Shannon

phyglory_rare_rel <- microbiome::transform(phyglory_rarefy, "compositional")
phyglory.ord.wuniR <- ordinate(phyglory_rare_rel, "PCoA", "unifrac", weighted=T) #this is how the pcoa was generated, the same one as in the main text
str(phyglory.ord.wuniR)
phyglory.ord.wuniR$values
phyglory.ord.wuniR$vectors #numbers from first 3 pcoa axes- CHECK THIS IS WHAT I WANT
metadataphyR$PCoA_axis1<-phyglory.ord.wuniR$vectors[,1]
metadataphyR$PCoA_axis2<-phyglory.ord.wuniR$vectors[,2]
metadataphyR$PCoA_axis3<-phyglory.ord.wuniR$vectors[,3]
metadataRH2<-as.data.frame(as(metadataphyR, "matrix")) #save phyloseq object as dataframe

str(metadataRH2)
metadataRH2$ObservedRich<-as.integer(metadataRH2$ObservedRich) #fix some of the salient categorization problems
metadataRH2$Shannon<-as.numeric(metadataRH2$Shannon)
metadataRH2$PCoA_axis1<-as.numeric(metadataRH2$PCoA_axis1)
metadataRH2$PCoA_axis2<-as.numeric(metadataRH2$PCoA_axis2)
metadataRH2$PCoA_axis3<-as.numeric(metadataRH2$PCoA_axis3)
metadataRH2$Germination_cohort<-as.factor(metadataRH2$Germination_cohort)
metadataRH2$Shape<-as.factor(metadataRH2$Shape)
metadataRH2$Line<-as.factor(metadataRH2$Line)
metadataRH2$Block<-as.factor(metadataRH2$Block)

hist(metadataRH2$ObservedRich)#check normality of data
hist(log(metadataRH2$ObservedRich)) 
hist(metadataRH2$Shannon)
hist(metadataRH2$PCoA_axis1)
hist(metadataRH2$PCoA_axis2)
hist(metadataRH2$PCoA_axis3)
```
Running the models
```{r}
#for our H2 estimates:
set.seed(0)
RH2_ObservedRich<-lmer(log(ObservedRich)~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
RH2_Shannon<-lmer(Shannon~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
RH2_PCoA1<-lmer(PCoA_axis1~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
RH2_PCoA2<-lmer(PCoA_axis2~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
RH2_PCoA3<-lmer(PCoA_axis3~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))

summary(RH2_ObservedRich) #sig germ
summary(RH2_Shannon)
summary(RH2_PCoA1) #sig germ
summary(RH2_PCoA2)#sig germ
summary(RH2_PCoA3) #sig M difference from H

Anova(lmer(log(ObservedRich)~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")), type=3)
Anova(lmer(Shannon~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")), type=3)
Anova(lmer(PCoA_axis1~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")), type=3)
Anova(lmer(PCoA_axis2~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")), type=3)
Anova(lmer(PCoA_axis3~ Germination_cohort + Shape + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")), type=3)
```
loglik with models not containing Line (higher(and less negative values) are better)
```{r}
set.seed(0)
logLik(RH2_ObservedRich)#-116.773
logLik(lmer(log(ObservedRich)~ Germination_cohort + Shape + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")))# -116.7835
logLik(RH2_Shannon)#-114.6886
logLik(lmer(Shannon~ Germination_cohort + Shape + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")))#-114.7927
logLik(RH2_PCoA1)# 265.7301 
logLik(lmer(PCoA_axis1~ Germination_cohort + Shape + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")))# 265.6788
logLik(RH2_PCoA2)# 329.5705
logLik(lmer(PCoA_axis2~ Germination_cohort + Shape + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead")))# 329.5705
logLik(RH2_PCoA3) #422.3402
logLik(lmer(PCoA_axis3~ Germination_cohort + Shape + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))) #422.208
#including line gives a better likelihood score except for Pcoa axis 2, which has same likelihood
```
### Extract variance components and calculate heritability
```{r}
print(VarCorr(RH2_ObservedRich), comp=c("Variance", "Std.Dev."))#example output from VarCorr

communityphenoR<-c(RH2_ObservedRich, RH2_Shannon, RH2_PCoA1, RH2_PCoA2, RH2_PCoA3)
comphenlistR<-lapply(communityphenoR, function(x) as.data.frame(VarCorr(x))[,c("vcov", "sdcor")])
comphenframeR<- data.frame(matrix(unlist(comphenlistR), nrow=length(comphenlistR), byrow=TRUE))
colnames(comphenframeR)<-c("Line_variance","Block_variance", "Residual_variance","Line_stdev","Block_stdev", "Residual_stdev")
rownames(comphenframeR)<-c("Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3")
comphenframeR<-comphenframeR %>% 
  mutate(Total_variance= Line_variance+Block_variance+Residual_variance,
         LinePercent=Line_variance/Total_variance,
         BlockPercent=Block_variance/Total_variance,
        ResidualPercent=Residual_variance/Total_variance )
comphenframeR
comphenPERCENTR<-gather(comphenframeR, key="Variance_component", value="Percent_variance_explained", 8:10)
comphenPERCENTR$Model<-c("Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3", "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3", "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3") 
head(comphenframeR)
comphenPERCENTR
```
figure
```{r}
comphenPERCENTR$Model<-factor(comphenPERCENTR$Model, levels=c( "PCoA3", "Shannon","PCoA1", "Observed_Richness", "PCoA2"))
communityphenotypes<-comphenPERCENTR %>% 
  filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x = Model, y = Percent_variance_explained, fill=Variance_component)) +
 geom_bar(stat ="identity",width=0.5) +
 coord_flip() +
 labs(x = "Community phenotype", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial Block", "Plant Line"),  values = c("#FF6699", "#3399FF", "#E69F00")) +theme_cowplot() +theme(legend.position = "none")+scale_x_discrete(labels=c("PCoA axis 3","Shannon diversity","PCoA axis 1","Observed richness", "PCoA axis 2"))
communityphenotypes
```

### code for figure comparing magnitude of line vs shape
```{r}
#for figure purposes, comparing the magnitude of effect of line vs leaf shape:
set.seed(0)
fig_ObservedRich<-lmer(log(ObservedRich)~ Germination_cohort + (1|Shape) + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
fig_Shannon<-lmer(Shannon~ Germination_cohort + (1|Shape) + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
fig_PCoA1<-lmer(PCoA_axis1~ Germination_cohort + (1|Shape) + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
fig_PCoA2<-lmer(PCoA_axis2~ Germination_cohort + (1|Shape) + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))
fig_PCoA3<-lmer(PCoA_axis3~ Germination_cohort + (1|Shape) + (1|Line) + (1|Block), data=metadataRH2, control = lmerControl(optimizer ="Nelder_Mead"))

summary(fig_ObservedRich)
summary(fig_Shannon)
summary(fig_PCoA1) #
summary(fig_PCoA2)
summary(fig_PCoA3)

communityphenofig<-c(fig_ObservedRich, fig_Shannon, fig_PCoA1, fig_PCoA2, fig_PCoA3)
comphenlistfig<-lapply(communityphenofig, function(x) as.data.frame(VarCorr(x))[,c("vcov", "sdcor")])
comphenframefig<- data.frame(matrix(unlist(comphenlistfig), nrow=length(comphenlistfig), byrow=TRUE))
colnames(comphenframefig)<-c("Line_variance","Block_variance","Shape_variance", "Residual_variance","Line_stdev","Block_stdev","Shape_stdev", "Residual_stdev")
rownames(comphenframefig)<-c("Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3")
comphenframefig<-comphenframefig %>% 
  mutate(Total_variance= Line_variance+Block_variance+Shape_variance+Residual_variance,
         LinePercent=Line_variance/Total_variance,
         BlockPercent=Block_variance/Total_variance,
         ShapePercent=Shape_variance/Total_variance,
         GeneticPercent=(Line_variance+Shape_variance)/Total_variance,
        ResidualPercent=Residual_variance/Total_variance )
comphenframefig
comphenPERCENTfig<-gather(comphenframefig, key="Variance_component", value="Percent_variance_explained", 10:14)
comphenPERCENTfig$Model<-c("Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3", "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3", "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3", "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3",  "Observed_Richness", "Shannon", "PCoA1", "PCoA2", "PCoA3")
head(comphenframefig)
```
magnitude figure
```{r}
comphenPERCENTfig$Model<-factor(comphenPERCENTfig$Model, levels=c( "PCoA3", "Shannon","PCoA1", "Observed_Richness", "PCoA2"))
comphenPERCENTfig$Variance_component <- factor(comphenPERCENTfig$Variance_component, levels = c("BlockPercent","ShapePercent", "LinePercent", "ResidualPercent", "GeneticPercent"))
communityphenotypesfig<-comphenPERCENTfig %>% 
  filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x = Model, y = Percent_variance_explained, fill=Variance_component)) +
 geom_bar(stat ="identity",width=0.5) +
 coord_flip() +
 labs(x = "Community phenotype", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Leaf shape genotype","Plant line"),  values = c("#FF6699","#E69F00", "#3399FF","#99CC00")) +theme_cowplot()  +theme(legend.position = "none")+scale_x_discrete(labels=c("PCoA axis 3","Shannon diversity","PCoA axis 1","Observed richness", "PCoA axis 2"))
communityphenotypesfig
```

## Genera CLR transformed
```{r}
metadataH2<-as.data.frame(sample_data(phyglory))
write.csv(metadataH2, "metadataH2.csv")
metadataH2<-read.csv('metadataH2.csv',row.names = 1, header = TRUE)#to get it as a dataframe, not neccessary for the model though, it can be left in phyloseq-ish format
metadataH2$Germination_cohort<-as.factor(metadataH2$Germination_cohort)
metadataH2$Shape<-as.factor(metadataH2$Shape)
metadataH2$Line<-as.factor(metadataH2$Line)
metadataH2$Block<-as.factor(metadataH2$Block)
metadataH2 #this metadata has corresponding rows to the feature table (100, 101, 102... 10 etc.)

str(metadataH2)
metadataH2
```
### Models and figure
```{r}
featuretableCLRgen
my_lmersCLR <- lapply(1:15, function(x) lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +metadataH2$Shape + (1|metadataH2$Line) + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))) 

# call the summaries of the list of regressions and make a dataframe:
summariesCLR <- lapply(my_lmersCLR, summary)
head(summariesCLR)
# list of only main coefficents with estimates and with p values for ipomoeajuice:
summaries_subset_listCLR<- lapply(summariesCLR, function(x) x$coefficients[, c(1,5)])
head(summaries_subset_listCLR)
summaries_subset_frameCLR <- data.frame(matrix(unlist(summaries_subset_listCLR), nrow=length(summaries_subset_listCLR), byrow=TRUE))
colnames(summaries_subset_frameCLR) <- c("Intercept_estimate","Germ_cohort_estimate","ShapeL_estimate","ShapeM_estimate","Intercept_pvalue", "Germ_cohort_pvalue", "ShapeL_pvalue", "ShapeM_pvalue")
head(summaries_subset_frameCLR)

#VarCorr to extract random effects 
summaries_subset_var_listCLR<-lapply(my_lmersCLR, function(x) as.data.frame(VarCorr(x))[,c("vcov", "sdcor")])
summaries_subset_var_frameCLR<- data.frame(matrix(unlist(summaries_subset_var_listCLR), nrow=length(summaries_subset_var_listCLR), byrow=TRUE))
head(summaries_subset_var_frameCLR)
colnames(summaries_subset_var_frameCLR)<-c("Line_variance","Block_variance","Residual_variance","Line_stdev","Block_stdev","Residual_stdev")
head(summaries_subset_var_frameCLR)

#Running type 3 anovas on the models to get F test statistics for shape
type3_lmersCLR<-lapply(1:15, function(x) Anova((lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +metadataH2$Shape + (1|metadataH2$Line) + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))), type=3))
type3_lmersCLR
type3_lmers_frameCLR<-data.frame(matrix(unlist(type3_lmersCLR), nrow=length(type3_lmersCLR), byrow=TRUE))
type3_lmers_frameCLR
colnames(type3_lmers_frameCLR) <- c("Intercept_Chisq","Germ_cohort_Chisq","Shape_Chisq","Intercept_df", "Germ_cohort_df","Shape_df", "Intercept_pvalue", "Germ_cohort_pvalue", "Shape_pvalue" )
Germ_cohort_anovap<-type3_lmers_frameCLR[,8]
Leafshape_anovap<-type3_lmers_frameCLR[,9]

summaries_outputCLR<-cbind(summaries_subset_frameCLR, summaries_subset_var_frameCLR) #combine fixed and random outputs
summaries_output_fullCLR<-cbind(summaries_outputCLR, Germ_cohort_anovap)
summaries_output_fullCLR<-cbind(summaries_output_fullCLR, Leafshape_anovap)
genus<-colnames(featuretableCLRgen)
model_number<-seq(1:500)
summaries_output_fullCLR$Genus<-genus[1:15] #connect model outputs to the ASV it was run on
summaries_output_fullCLR$Model_number<-model_number[1:15] #keep track of what model output we're looking at. Doubles as commonness of ASV
summaries_output_fullCLR
ipomoeajuiceCLR<-summaries_output_fullCLR

ipomoeajuiceCLR<-ipomoeajuiceCLR %>%  
  mutate(Total_variance= Line_variance+Block_variance+Residual_variance,
         LinePercent=Line_variance/Total_variance,
         BlockPercent=Block_variance/Total_variance,
        ResidualPercent=Residual_variance/Total_variance )
ipomoeajuiceCLR
ipomoeaPERCENTCLR<-gather(ipomoeajuiceCLR, key="Variance_component", value="Percent_variance_explained", 19:21)
ipomoeaPERCENTCLR<-ipomoeaPERCENTCLR %>% 
  mutate(Line_percent=(Line_variance)/Total_variance)

genera<-ipomoeaPERCENTCLR %>% 
   filter(!Variance_component %in% c('ResidualPercent', 'Line_percent')) %>% 
  ggplot(aes(x=reorder(Genus, -Line_percent), y=Percent_variance_explained,fill=Variance_component))+
 geom_bar(stat ="identity",width=.75) +
 coord_flip() +
 labs(x = "Genus", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Plant line"),  values = c("#FF6699", "#3399FF", "#E69F00")) +theme_cowplot() 
genera
```
### log likelihood for H2 models
```{r}
my_lmers_likelihood <-lapply(1:15, function(x) logLik( lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +metadataH2$Shape + (1|metadataH2$Line) + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))) )

my_lmers_likelihood_noline <- lapply(1:15, function(x) logLik( lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +metadataH2$Shape + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))) )

my_lmers_likelihood_frame<-data.frame(matrix(unlist(my_lmers_likelihood), nrow=length(my_lmers_likelihood), byrow=TRUE))
my_lmers_likelihood_noline_frame<-data.frame(matrix(unlist(my_lmers_likelihood_noline), nrow=length(my_lmers_likelihood_noline), byrow=TRUE))

colnames(my_lmers_likelihood_frame) <- c("With_random_effects_logLik")
colnames(my_lmers_likelihood_noline_frame) <- c("Noline_logLik")

LogLikelihood_comparison<-cbind(my_lmers_likelihood_frame, my_lmers_likelihood_noline_frame)
LogLikelihood_comparison$Model_number<-model_number[1:15]
LogLikelihood_comparison$Genus<-genus[1:15]

LogLikelihood_comparison<-LogLikelihood_comparison %>% mutate(Difference_noline_or_fullrandom= With_random_effects_logLik-Noline_logLik)#if 'noline' is more more negative/worse, then the value will be positive, positive value means line improved fit
View(LogLikelihood_comparison)
LogLikelihood_comparison %>% 
  ggplot(aes(x=Genus, y=Difference_noline_or_fullrandom, color=ifelse(Difference_noline_or_fullrandom >0, "Improves model fit", "Same or worse model fit")))+
  geom_point()+  scale_color_manual(name="Effect of including line", values= c("red", "black"))+ xlab('Genus') +ylab('Log likelihood difference') +theme_bw()+theme(axis.text.x = element_text(size=10, angle = 45, hjust = 1))
#in almost all cases, including line makes little difference, but it does affect some ASVs more than others, especially the most common of the most common. Model number 1 indicates the most common ASV in the dataset. 
LogLikelihood_comparison %>% 
  filter(Difference_noline_or_fullrandom>0)#positive value means line improved fit
LogLikelihood_comparison %>% 
  filter(Difference_noline_or_fullrandom<0) #very slight worse fit, but the same to 4 decimals
LogLikelihood_comparison %>% 
  filter(Difference_noline_or_fullrandom==0) # exact same fit
```

### magnitude line vs leaf shape models and figure
```{r}
featuretableCLRgen
my_lmersfig <- lapply(1:15, function(x) lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +(1|metadataH2$Shape) + (1|metadataH2$Line) + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))) 

# call the summaries of the list of regressions and make a dataframe:
summariesfig <- lapply(my_lmersfig, summary)
summariesfig
# list of only main coefficents with estimates and with p values for ipomoeajuice:
summaries_subset_listfig<- lapply(summariesfig, function(x) x$coefficients[, c(1,5)])
head(summaries_subset_listfig)
summaries_subset_framefig <- data.frame(matrix(unlist(summaries_subset_listfig), nrow=length(summaries_subset_listfig), byrow=TRUE))
colnames(summaries_subset_framefig) <- c("Intercept_estimate","Germ_cohort_estimate","Intercept_pvalue", "Germ_cohort_pvalue" )
head(summaries_subset_framefig)

#VarCorr to extract random effects 
summaries_subset_var_listfig<-lapply(my_lmersfig, function(x) as.data.frame(VarCorr(x))[,c("vcov", "sdcor")])
summaries_subset_var_framefig<- data.frame(matrix(unlist(summaries_subset_var_listfig), nrow=length(summaries_subset_var_listfig), byrow=TRUE))
head(summaries_subset_var_framefig)
colnames(summaries_subset_var_framefig)<-c("Line_variance","Block_variance","Shape_variance", "Residual_variance","Line_stdev","Block_stdev","Shape_stdev", "Residual_stdev")
head(summaries_subset_var_framefig)

#Running type 3 anovas on the models to get F test statistics for shape
type3_lmersfig<-lapply(1:15, function(x) Anova((lmer(featuretableCLRgen[,x]~ metadataH2$Germination_cohort +(1|metadataH2$Shape) + (1|metadataH2$Line) + (1|metadataH2$Block), control = lmerControl(optimizer ="Nelder_Mead"))), type=3))
type3_lmers_framefig<-data.frame(matrix(unlist(type3_lmersfig), nrow=length(type3_lmersfig), byrow=TRUE))
type3_lmers_framefig
colnames(type3_lmers_framefig) <- c("Intercept_Chisq","Germ_cohort_Chisq","Intercept_df", "Germ_cohort_df", "Intercept_pvalue", "Germ_cohort_pvalue" )
Germ_cohort_anovap<-type3_lmers_framefig[,6]

summaries_outputfig<-cbind(summaries_subset_framefig, summaries_subset_var_framefig) #combine fixed and random outputs
summaries_output_fullfig<-cbind(summaries_outputfig, Germ_cohort_anovap)
genus<-colnames(featuretableCLRgen)
model_number<-seq(1:500)
summaries_output_fullfig$Genus<-genus[1:15] #connect model outputs to the ASV it was run on
summaries_output_fullfig$Model_number<-model_number[1:15] #keep track of what model output we're looking at. Doubles as commonness of ASV
summaries_output_fullfig
ipomoeajuicefig<-summaries_output_fullfig

ipomoeajuicefig<-ipomoeajuicefig %>%  
  mutate(Total_variance= Line_variance+Block_variance+Shape_variance+Residual_variance,
         LinePercent=Line_variance/Total_variance,
         BlockPercent=Block_variance/Total_variance,
         ShapePercent=Shape_variance/Total_variance,
         GeneticPercent=(Line_variance+Shape_variance)/Total_variance,
        ResidualPercent=Residual_variance/Total_variance )
ipomoeajuicefig
ipomoeaPERCENTfig<-gather(ipomoeajuicefig, key="Variance_component", value="Percent_variance_explained", 17:21)
ipomoeaPERCENTfig<-ipomoeaPERCENTfig %>% 
  mutate(Genetic_percent=(Line_variance+Shape_variance)/Total_variance)
ipomoeaPERCENTfig<-ipomoeaPERCENTfig %>% 
  mutate(Line_percent=(Line_variance)/Total_variance)
ipomoeaPERCENTfig
ipomoeaPERCENTfig$Variance_component <- factor(ipomoeaPERCENTfig$Variance_component, levels = c("BlockPercent","ShapePercent", "LinePercent", "ResidualPercent", "GeneticPercent"))
ipomoeaPERCENTfig$Variance_component

generafig<-ipomoeaPERCENTfig %>% 
   filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x=reorder(Genus, -Line_percent), y=Percent_variance_explained,fill=Variance_component))+
 geom_bar(stat ="identity",width=.75) +
 coord_flip() +
 labs(x = "Genus", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Leaf shape genotype","Plant line"),  values = c("#FF6699","#E69F00", "#3399FF","#99CC00")) +theme_cowplot() 
generafig
```

# Figures
ancom figure
```{r}
ggsave2("ancomglory_shape_plot.png", ancomglory_shape_plot, dpi=600, width=7, height=5)
ancomglory_shape_plot
```

composition barplot
```{r}
multi_leaf <- (leaf_germ1 + leaf_germ2 ) + 
  plot_layout(nrow=1)+
  plot_annotation(tag_levels = list(c("A", "B"))) #add figure labels
multi_leaf #save 5 by 15
```

succession figure
```{r}
#possible succession figure
a.divglory+(b.div.wuniglory_rareG/b.div.wuniglory_rare)+plot_annotation(tag_levels="A") #save 6 by 10
```

heritability figure
```{r}
plot_grid(communityphenotypes,genera, labels="AUTO" , rel_widths = 2:3) #save 5 by 10 inches
```

magnitude of line vs shape figure
```{r}
plot_grid(communityphenotypesfig,generafig, labels="AUTO" , rel_widths = 2:3) #save 5 by 10 inches
```
all heritability figures?
```{r}
communityphenotypes<-comphenPERCENTR %>% 
  filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x = Model, y = Percent_variance_explained, fill=Variance_component)) +
 geom_bar(stat ="identity",width=0.5) +
 coord_flip() +
 labs(x = "Community phenotype", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial Block", "Plant Line"),  values = c("#FF6699", "#3399FF", "#E69F00")) +theme_cowplot() +theme(legend.position = "none")+scale_x_discrete(labels=c("PCoA axis 3","Shannon diversity","PCoA axis 1","Observed richness", "PCoA axis 2"))+ylim(0,0.15)
communityphenotypes
communityphenotypesfig<-comphenPERCENTfig %>% 
  filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x = Model, y = Percent_variance_explained, fill=Variance_component)) +
 geom_bar(stat ="identity",width=0.5) +
 coord_flip() +
 labs(x = "Community phenotype", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Leaf shape genotype","Plant line"),  values = c("#FF6699","#E69F00", "#3399FF","#99CC00")) +theme_cowplot()  +theme(legend.position = "none")+scale_x_discrete(labels=c("PCoA axis 3","Shannon diversity","PCoA axis 1","Observed richness", "PCoA axis 2"))+ylim(0,0.15)
communityphenotypesfig
genera<-ipomoeaPERCENTCLR %>% 
   filter(!Variance_component %in% c('ResidualPercent', 'Line_percent')) %>% 
  ggplot(aes(x=reorder(Genus, -Line_percent), y=Percent_variance_explained,fill=Variance_component))+
 geom_bar(stat ="identity",width=.75) +
 coord_flip() +
 labs(x = "Genus", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Plant line"),  values = c("#FF6699", "#3399FF", "#E69F00")) +theme_cowplot() +ylim(0,0.13)
genera
generafig<-ipomoeaPERCENTfig %>% 
   filter(!Variance_component %in% c('ResidualPercent', 'GeneticPercent')) %>% 
  ggplot(aes(x=reorder(Genus, -Line_percent), y=Percent_variance_explained,fill=Variance_component))+
 geom_bar(stat ="identity",width=.75) +
 coord_flip() +
 labs(x = "Genus", y = "Percent variance explained")+scale_fill_manual(name="Variance component", labels=c("Spatial block", "Leaf shape genotype","Plant line"),  values = c("#FF6699","#E69F00", "#3399FF","#99CC00")) +theme_cowplot()  +ylim(0,0.13)
generafig

plot_grid((communityphenotypes),genera,(communityphenotypesfig),generafig, labels="AUTO" , rel_widths = 2:3)
```

pcoa figure
```{r}
plot_grid(b.div.wuniglory_rareG, b.div.wuniglory_rare,b.div.wuniglory_methylo,b.div.wuniglory_sphingo,b.div.wuniglory_art, b.div.wuniglory_dein, ncol=2, labels="AUTO") #save 8 by 13 for only taxa. With other plots save 13x13
```

# Supplemental figures
leaf morphology 
```{r}
plot_grid(area,circularity, labels="AUTO", rel_widths = 3:2) #save 5 by 10 inches
```

relative abundances and regressions
```{r}
a<-phyglory_rel_rare %>% 
  psmelt() %>% 
  ggplot(aes(x=Methylobacterium_relabundance, y=Sphingomonas_relabundance))+geom_point()+geom_smooth(method='lm')+ylab("Sphingomonas relative abundance" )+xlab("Methylobacterium relative abundance")+theme_cowplot()

b<-ggplot(aes(x=PCoA_axis1, y=sample_data(phyglory_rel_rare)$Methylobacterium_relabundance), data=metadataphyR)+geom_point()+geom_smooth(method='lm')+xlab("Axis 1 [53.2%]")+ylab("Relative abundance")+theme_cowplot()+ggtitle("Methylobacterium")
c<-ggplot(aes(x=PCoA_axis2, y=sample_data(phyglory_rel_rare)$Sphingomonas_relabundance), data=metadataphyR)+geom_point()+geom_smooth(method='lm')+xlab("Axis 2 [23.2%]")+ylab("Relative abundance")+theme_cowplot()+ggtitle("Sphingomonas")

bc <-(b/c+plot_annotation(tag_levels = list(c("B", "C"))))
plot_grid(a+(bc))
a+bc #saved 5x8
```

